Response to the defense feedback

### 2021-06-18 Chapter-1/Chapter-1.tex
Updates from Overleaf

\chapter{Introduction} \label{chapter1}
Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with around one hundred thousand lines of code. 
Today, a mobile instant messaging application such as Telegram~\cite{telegram} contains more than two million lines of code. It is estimated that engineers built Google's infrastructure with 2 billion lines of code~\cite{potvin2016google}. The complexity in today's software systems makes it hard for developers to understand the codebase and find defects manually. So an automated bug detection tool is often needed. In this dissertation, we present techniques to analyze side-channel vulnerabilities in real-world applications. The side-channel vulnerability is a type of information leakage bug in software systems. Unlike many ordinary bugs, attackers exploit side-channel vulnerabilities from the implementation of the software rather than weaknesses in the implementation itself. So it is sometimes harder for developers to identify these vulnerabilities.

>>>>

\chapter{Introduction} \label{chapter1}
Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with less than one hundred thousand lines of code. 
Today, a mobile instant messaging application such as Telegram~\cite{telegram} contains more than two million lines of code. It is estimated that engineers built Google's infrastructure with 2 billion lines of code~\cite{potvin2016google}. The complexity in today's software systems makes it hard for developers to understand the codebase and find defects manually. So an automated bug detection tool is often needed. In this dissertation, we present techniques to analyze side-channel vulnerabilities in real-world applications. The side-channel vulnerability is a type of information leakage bugs in software systems. Unlike many ordinary bugs, attackers exploit side-channel vulnerabilities from the implementation of the software rather than weaknesses in the implementation itself. So it is sometimes harder for developers to identify these vulnerabilities.
